Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-04-03 trunk/constantRate/ConstCompFuzzExt-eprint.tex

\section*{Acknowledgements}
The authors are grateful to Nir Bitanski, Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants XXXX. The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.  
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\section*{Acknowledgements}
The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants XXXX. 
Omer Paneth is supported by the Simons award for graduate students in theoretical computer science and an NSF Algorithmic foundations grant 1218461.
The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
\bibliographystyle{alpha}
\bibliography{crypto}
